---
title: "p8105_hw3_yy2912"
output: github_document
---
```{r setup, include=FALSE}
devtools::install_github("thomasp85/patchwork")
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

#question 1: load instacart data 
```{r}
library(p8105.datasets)
data("instacart")
```
There are `r nrow(instacart)` rows and `r ncol(instacart)` columns in data 'instacart'.
There are `r nrow(distinct(instacart, aisle))` distinct aisel. 
Some key variables include `r nrow(distinct(instacart, order_id))` distinct order_id and `r nrow(distinct(instacart, user_id))` distinct user_id.

#question 1: how many aisles are there, and which aisles are the most items ordered from?
```{r}
numberof_aisle=
instacart %>%
  group_by(aisle) %>%
  summarize(n=n())%>%
  arrange(desc(n))
```
There are 134 aisles and most items are orderd from "fresh vegetables".

#question 1: make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered
```{r}
plot_aisle =
  numberof_aisle %>%
  filter(n>10000)%>%
  ggplot(aes(x=n, y=aisle))
plot_aisle+geom_point()+theme(
          legend.position="none") +
  xlab("Aisle")+
  ylab("The number of items ordered") +
  ggtitle("The number of items ordered in each aisle")
```

#question 1: make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
popular_item=
  instacart %>%
  filter(aisle == c("baking ingredients","dog food care","packaged vegetables fruits"))%>%
  group_by(product_name, aisle)%>%
  summarize(
    n = n()
  ) %>% 
 group_by(aisle) %>% 
  summarize(
    rank=max(n))%>%
  top_n(3)%>%
  knitr::kable()
```

#question 1: make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week.
```{r}
instacart %>%
  filter(product_name==c("Pink Lady Apples","Coffee Ice Cream"))%>%

  group_by(product_name, order_dow)%>%
  summarize(mean_hour=mean(order_hour_of_day))%>%
  knitr::kable()
```

#question 2: 
```{r}
library(p8105.datasets)
data("brfss_smart2010")
brfss = janitor::clean_names(brfss_smart2010) %>% 
  mutate(
    response = factor(response, levels = c("Poor", "Fair", "Good", "Very Good", "Excellent"))
    )
```
#question 2: format the data to use appropriate variable names;focus on the “Overall Health” topic; include only responses from “Excellent” to “Poor”; organize responses as a factor taking levels ordered from “Poor” to “Excellent”
```{r}
brfss %>%
  filter(
    topic == "Overall Health",
    response == c("Excellent", "Very good", "Good", "Fair", "Poor")
  ) %>% 
  arrange(response) 
```
#question 2: In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
sevenormore_location=
  brfss %>% 
  filter(year == 2002) %>% 
  group_by(locationabbr) %>% 
  summarize(
    n = n()
  ) %>% 
  filter(n >= 7) %>% 
  arrange(n) 
```
In 2002, the 7 states that were observed at 7 or more locations are RI, GA,	ME, OH, MA, NJ, and PA. 

```{r}
sevenormore_location=
  brfss %>% 
  filter(year == 2010) %>% 
  group_by(locationabbr) %>% 
  summarize(
    n = n()
  ) %>% 
  filter(n >= 7) %>% 
  arrange(n) 
```
In 2010, the 15 states that were observed at 7 or more locations are NC, PA, OH, SC, UT, CO, ID, MA, ME, TN, NY, CA, MD, TX, and FL. 

#question 2: Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. 
```{r}
brfss_new =
  brfss %>% 
  filter(response == "Excellent") %>% 
  group_by(year, locationabbr) %>% 
  mutate(mean = mean(data_value, na.rm = FALSE)) %>%
  select(year, locationabbr, mean) %>% 
  distinct() 
```
#question 2: Make a “spaghetti” plot of this average value over time within a state.
```{r}
  ggplot(brfss_new, aes(x = year, y = mean, color = locationabbr, group = locationabbr))+
  geom_line() +
  theme(legend.position="none") +
  xlab("Year") +
  ylab("The average value within a state") +
  ggtitle("The average value over time within a state")
```

#question 2: Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

response_2006 = 
  brfss %>% 
  filter(year == 2006) %>% 
  ggplot(aes(x = data_value, fill = response)) +
  geom_density(color=data_value, alpha = .5) +
  theme(legend.position = "bottom")


```{r}
response_2006 = 
  brfss %>% 
  filter(year == 2006) %>% 
  ggplot(aes(x = data_value, fill = response)) +
  geom_density(alpha = .5) +
  theme(legend.position = "bottom")+
	viridis::scale_fill_viridis(discrete = TRUE)

```

```{r}
response_2010 = 
  brfss %>% 
  filter(year == 2010) %>% 
  ggplot(aes(x = data_value, fill = response)) +
 geom_density(alpha = .5) +
  theme(legend.position = "bottom")+
	viridis::scale_fill_viridis(discrete = TRUE)
 
```

```{r}
library(patchwork)
(response_2006 + response_2010)
```

#question 3: Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
accel_data = read_csv(file = "./data/accel_data.csv")%>% 
janitor::clean_names() 
```

```{r}
accel_data_tidy = 
        accel_data %>% 
        pivot_longer(
        activity_1:activity_1440,
        names_to = "activity",
        values_to = "activity_minutes"
    ) %>%
  
   mutate(
      day = factor(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday" )), 
      weekend = day %in% c("Saturday", "Sunday")
    ) %>% 
 
 mutate(
    week = as.integer(week),
    day_id = as.integer(day_id),
    day = as.character(day),
    activity = as.character(activity),
    activity_minutes = as.numeric(activity_minutes),
    weekend = as.numeric(weekend)
  )
```  
The variables in the tidied dataset include: `r ls(accel_data_tidy)` and there are `r nrow(accel_data_tidy)` observations in the dataset.

#question 3: Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?
```{r}
accel_data_tidy %>% 
  group_by(day_id) %>% 
  mutate(total_activity = sum(activity_minutes)) %>%
  select(week, day_id, day, weekend, total_activity) %>% 
  distinct() %>% 
  knitr::kable()
  
```

There is not any apparent trend from the table generated. Each week has different activity minutes from Monday to Sunday. 


